---
title: "Covid-19 trends"
author: "Julia Lunardi"
date: "3/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Investigating Covid-19 trends

This is a project focused on exploring and deriving insights from the Covid-19 
dataset provided by kaggle. I intend, specifically, to analyze the geographical
distribution of cases, and the least ratio of deaths by positive cases. 

Research question: Which countries have had the highest number of positive cases against the number of tests?

1. Loading packages
```{r}
library(tidyverse)
```

2. Reading in the data
```{r}
covid_df<- read_csv(file.choose())

```

3. First look at the data
```{r}
glimpse(covid_df)
```

```{r}
dim(covid_df)
```


```{r}
vector_cols <- colnames(covid_df)

vector_cols
```


```{r}
head(covid_df)
```

Province_state is "All states" when there's no state/province data. Since the goal
is to analyze country-level data, an approach is to filter province_state and take
only the values "All states".

4. Extracting only country-level data

```{r}
covid_df_all_states <- covid_df %>%
    filter(Province_State == "All States")

covid_df <- covid_df[-5]

```

```{r}
covid_df_all_states
```


5. Working with daily data: filtering out cumulative data

```{r}
covid_df_all_states_daily <- covid_df_all_states %>%
    select(Date, Country_Region, active, hospitalizedCurr, daily_tested, daily_positive)

covid_df_all_states_daily
```


6. Extracting top ten cases countries data

```{r}
covid_df_all_states_daily_sum <- covid_df_all_states_daily %>%
  group_by(Country_Region) %>%
  summarize( 
    tested = sum(daily_tested),
    positive = sum(daily_positive),
    active = sum(active),
    hospitalized = sum(hospitalizedCurr)
    ) %>%
  arrange(-tested)

covid_df_all_states_daily_sum
```


```{r}
covid_top_10 <- head(covid_df_all_states_daily_sum, 10)

covid_top_10
```



7. Which countries have had the highest number of positive cases against the number of tests?

```{r}
countries <- covid_top_10$Country_Region

tested_cases <- covid_top_10$tested

positive_cases <- covid_top_10$positive

active_cases <- covid_top_10$active

hospitalized_cases <- covid_top_10$hospitalized

```



```{r}
names(tested_cases) <- countries

names(positive_cases) <- countries

names(active_cases) <- countries

names(hospitalized_cases) <- countries


```


```{r}
positive_tested_top_3 <- positive_cases/tested_cases

sort(positive_tested_top_3, decreasing = TRUE)
```


8.  Keep all the information available for the top three countries that have had the highest number of positive cases against the number of tests.

```{r}
united_kingdom <- c(0.11, 1473672, 166909, 0, 0)

united_states <- c(0.10, 17282363, 1877179, 0, 0)

turkey <- c(0.08, 2031192, 163941, 2980960, 0)
```



```{r}
covid_mat <- rbind(united_kingdom, united_states, turkey)

colnames(covid_mat) <- c("Ratio", "tested", "positive", "active", "hospitalized")

covid_mat

```


9. Put all our answers and datasets together

```{r}
question <- "Which countries have had the highest number of positive cases against the number of tests?"

answer <- c("Positive tested cases" = positive_tested_top_3)
```



```{r}
dataframes <- list(covid_df, covid_df_all_states, covid_df_all_states_daily, covid_top_10)

matrix <- list(covid_mat)

vectors <- list(vector_cols, countries)
```

```{r}
data_structure_list <- list(dataframes, matrix, vectors)

names(data_structure_list) <- c("dataframes", "matrix", "vectors")

data_structure_list

```


```{r}
covid_analysis_list <- list(question, answer, data_structure_list)

covid_analysis_list[[2]]
```



Based on these results, we can see that the countries with top positive/tested ratio within
the analyzed period were United States, United Kingdom, and Turkey. Furthermore, the United States, Russia and Italy
have cumulatively the largest amount of positive cases.s



