---
title: "Covid-19 trends"
author: "Julia Lunardi"
date: "3/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Investigating Covid-19 trends

This is a project focused on exploring and deriving insights from the Covid-19 
dataset provided by kaggle. I intend, specifically, to analyze the geographical
distribution of cases, and the least ratio of deaths by positive cases. 

1. Loading packages
```{r}
library(tidyverse)
```

2. Reading in the data
```{r}
covid_df<- read_csv(file.choose())

```

3. First look at the data
```{r}
glimpse(covid_df)
```

```{r}
dim(covid_df)
```


```{r}
vector_cols <- colnames(covid_df)

vector_cols
```


```{r}
head(covid_df)
```

Province_state is "All states" when there's no state/province data. Since the goal
is to analyze country-level data, an approach is to filter province_state and take
only the values "All states".

4. Extracting only country-level data

```{r}
covid_df_all_states <- covid_df %>%
    filter(Province_State == "All States") %>%
    covid_df[-5]
```


5. Working with daily data: filtering out cumulative data

```{r}
covid_df_all_states_daily <- covid_df_all_states %>%
    select(Date, Country_Region, active, hospitalizedCurr, daily_tested, daily_positive)
```


6. Extracting top ten cases countries data



